### 2023-05-24 paper/Chapters/Chapter1.tex
Updates for the paper

As reported by \textcite{duisterhofTartanCalibIterativeWideAngle2022} on
\citedate{duisterhofTartanCalibIterativeWideAngle2022}, the current state-of-the-art
methods
\cite{olsonAprilTagRobustFlexible2011}
\cite{schopsWhyHaving102020} \cite{krogiusFlexibleLayoutsFiducial2019}
fail on images with high distortion.
\textcite{duisterhofTartanCalibIterativeWideAngle2022} suggested an iterative
the approach of image undistortion and target reprojection, achieving the superior
robustness to the noise than the state-of-the-art methods because the feature
detection is performed on the undistorted image.

Instead of searching for the features on the undistorted image, it is possible to
use conjugate translations \cite{schaffalitzkyGeometricGroupingRepeated1998},
to predict the position of the previously undetected feature points and to
further, constrain the camera calibration.
\textcite{prittsMinimalSolversRectifying2021} showed that three pairs of points,
related by the same translations on the scene plane are sufficient to estimate
the camera calibration and the parameters of the conjugate translations.

We want to use the work of \textcite{prittsMinimalSolversRectifying2021} to bootstrap
the camera calibration, and then use the found conjugate translations and camera
parameters to iteratively predict and refine the positions of the calibration
board features, calibration parameters, and conjugate translations.

>>>>

As reported by \textcite{duisterhofTartanCalibIterativeWideAngle2022} on
\citedate{duisterhofTartanCalibIterativeWideAngle2022}, the current state-of-the-art
methods
\cite{olsonAprilTagRobustFlexible2011a}
\cite{schopsWhyHaving102020} \cite{krogiusFlexibleLayoutsFiducial2019}
fail on images with high distortion.
\textcite{duisterhofTartanCalibIterativeWideAngle2022} suggested an iterative
the approach of image undistortion and target reprojection, achieving the superior
robustness to the noise than the state-of-the-art methods because the feature
detection is performed on the undistorted image.
% \todo{Probably remove the emphasis on TartanCalib, if I am not going to compare
% with it}

Instead of searching for the features on the undistorted image from scratch, it
is possible to utilize the prior knowledge of the geometry of the calibration
board, effectively predicting the possible positions of previously undetected
features. It can be done by projecting the board onto the image using the
intermediate camera calibration, and then filtering the possible positions in
order to eliminate false positives.

This additional points will further constrain the camera calibration, improving
the accuracy of the calibration parameters.
\todo{Explain why more features is better}
\missingfigure{Show the example of the calibration board and the image}

### 2023-05-24 paper/paper.tex
Paper updates
Updates for the paper

\usepackage{todonotes}

@@

@@

\begin{declaration}
	\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
	\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

	\begin{itemize}
		\item This work was done wholly or mainly while in candidature for a research degree at this University.
		\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
		\item Where I have consulted the published work of others, this is always clearly attributed.
		\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
		\item I have acknowledged all main sources of help.
		\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
	\end{itemize}

	\noindent Signed:\\
	\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

	\noindent Date:\\
	\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

\cleardoublepage

@@

\vspace*{0.2\textheight}

\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak

\hfill Dave Barry

@@

	% Camera calibration is a crucial step in many computer vision applications.
	% However, despite the constant development of solutions, they still tend to
	% be sensitive to the noise of the input data, bad lightning conditions,
	% occlusions and other problems, especially under the conditions of
	% high distortion, such as mobile phones and GoPro-type cameras.
	%
	% In this paper, we propose a novel approach to camera calibration. We want to
	% use a robust solver to estimate the geometry between the correspondence of
	% points on the calibration pattern, which are called conjugate translations.
	% It is possible to use those
	% conjugate translations to predict the possible position of the previously
	% undetected calibration board features. We want to use the new points to constrain the camera calibration further. This process can be run iteratively,
	% refining the calibration board features, conjugate translations, and improving
	% the camera calibration.
\end{abstract}

@@

\begin{acknowledgements}
	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
	The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots

	\noindent If you was supported with the scholarship, please thank to your donor organization or a person who supported you.
\end{acknowledgements}

@@

\tableofcontents % Prints the main table of contents

\listoffigures % Prints the list of figures

\listoftables % Prints the list of tables

@@

\dedicatory{For/Dedicated to/To my\ldots}

@@

\include{Chapters/Chapter1}
%\include{Chapters/Chapter2} 
%\include{Chapters/Chapter3}
%\include{Chapters/Chapter4} 
%\include{Chapters/Chapter5}

>>>>

@@

\usepackage[textwidth=20mm]{todonotes}
\setlength{\marginparwidth}{2.5cm}
\usepackage{caption}
\usepackage{subcaption}
\graphicspath{ {images/} }

@@

% \begin{declaration}
% 	\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
% 	\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
%
% 	\begin{itemize}
% 		\item This work was done wholly or mainly while in candidature for a research degree at this University.
% 		\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
% 		\item Where I have consulted the published work of others, this is always clearly attributed.
% 		\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
% 		\item I have acknowledged all main sources of help.
% 		\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
% 	\end{itemize}
%
% 	\noindent Signed:\\
% 	\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
%
% 	\noindent Date:\\
% 	\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
% \end{declaration}
%
% \cleardoublepage
\todo{Enable}

@@

% \vspace*{0.2\textheight}
%
% \noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak
%
% \hfill Dave Barry
\todo{Enable}

@@

	Camera calibration is a crucial step in many computer vision applications.
  Typically, it involves taking a set of images of a calibration pattern,
  detecting its' features, and estimating the camera parameters. However, under
  certain conditions (including occlusions, bad lightning, highly distorted
  images etc.), feature detectors might fail to detect some of the
  features.\todo{Do I have to justify it?}.

  In this paper, we propose a novel approach to feature detection in the context
  of camera calibration. After the initial feature detection and calibration,
  we use the intermediate camera parameters to predict the possible positions
  of the previously undetected features. Those features are filtered using the
  binary classifier, and the remaining features are used to further constrain
  the camera calibration.

	% In this paper, we propose a novel approach to camera calibration. We want to
	% use a robust solver to estimate the geometry between the correspondence of
	% points on the calibration pattern, which are called conjugate translations.
	% It is possible to use those
	% conjugate translations to predict the possible position of the previously
	% undetected calibration board features. We want to use the new points to constrain the camera calibration further. This process can be run iteratively,
	% refining the calibration board features, conjugate translations, and improving
	% the camera calibration.
\end{abstract}

@@

% \begin{acknowledgements}
% 	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
% 	The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
%
% 	\noindent If you was supported with the scholarship, please thank to your donor organization or a person who supported you.
% \end{acknowledgements}
\todo{Enable}

@@

% \tableofcontents % Prints the main table of contents
\todo{Enable}
%
% \listoffigures % Prints the list of figures
\todo{Enable}
%
% \listoftables % Prints the list of tables
\todo{Enable}

@@

% \dedicatory{For/Dedicated to/To my\ldots}
\todo{Enable}

@@

\include{Chapters/Chapter1}
\include{Chapters/Chapter2} 
\include{Chapters/Chapter3}
\include{Chapters/Chapter4} 
\include{Chapters/Chapter5} 
\include{Chapters/Chapter6}
